---
title: "Participation 6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("exercise.R")
library(knitr)
```


1. Scatter plot of the entire diamond sample, graphed with carat on x and price 
on the y axis. The color each of the points is based on their clarity.

```{r , echo = FALSE}
entire_diamonds_clarity
```

2. Scatter plot of the diamond sample, graphed with carat on the x axis 
and cut on the y axis. The size of the dots are based on the price of the 
diamond. 

``` {r, echo = FALSE}
cut_by_carat
```

3. Smooth plot of the diamond sample, graphed with carat on the x axis, and
price on the y axis. The color is based on the cut of the diamond.

``` {r, echo = FALSE, message = FALSE}
smooth_plot
```

4. Bar plot of the diamond sample, graphed with cut on the x axis, and
frequency on the y axis.

``` {r, echo = FALSE}
bar_cut
```

5.  Histogram of the diamond sample, graphed with price on the x axis, and
frequency on the y axis. The color is based on the clarity of the diamond.

``` {r, echo = FALSE}
hist_prices_clarity
```

6.  Smooth and scatter plot of the diamond sample, graphed with carat on the x 
axis, and price on the y axis. The two colors differentiate the types of plots.

``` {r, echo = FALSE, message = FALSE}
diamond_sample_data
```